Rotation of Magnetic Islands in Tokamak Plasmas

### 2021-12-12 Research/NonlinearTearingModeTheory/NonlinearTearingModeTheory.tex
Latest version

\subsection{Perturbed Magnetic Field}\label{cyl}
Consider a tearing mode perturbation that has $m$ periods in the poloidal direction, and
$n$ periods in the toroidal direction. 
The perturbed magnetic field associated with the tearing mode is written $\delta{\bf B} \simeq \nabla\delta\psi\times{\bf e}_z$,  
where
$\delta\psi(r,\theta,\varphi,t)= \delta\psi(r,t)\,\exp[\,{\rm i}\,(m\,\theta-n\,\varphi)]$, 
and $\varphi=z/R_0$ is a simulated toroidal angle. 
Throughout most of the plasma $\delta\psi(r,t)$ satisfies the
{\em cylindrical tearing mode equation}:\cite{wes}
\begin{equation}\label{e3}
\frac{\partial^2\delta\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\delta\psi}{\partial r}-\frac{m^2}{r^2}\,\delta\psi - \frac{J_z'\,\delta\psi}{r\,(1/q-n/m)}=  0,
\end{equation}
where 
$J_z(r)= R_0\,\mu_0\,j_z(r)/B_z$,
and $j_z(r)$ is the equilibrium `toroidal' current density. Here, $'\equiv d/dr$.

@@

Note that Eq.~(\ref{e100}) is singular at the so-called {\em resonant}\/ magnetic flux-surface, radius $r=r_s$, at which 
$q(r_s)= m/n$. 
As is well-known, the general solution of Eq.~(\ref{e100} is such that $\delta\psi$ is continuous across the resonant surface,
whereas $\partial\delta\psi/\partial r$ is discontinuous. The discontinuity in $\partial \delta\psi/\partial r$ implies the presence of a helical  current sheet  at the resonant surface. 
The complex quantity 
\begin{equation}
{\mit\Psi}_s(t)= \delta\psi(r_s,t) 
\end{equation}
parameterizes the amplitude and phase of the
reconnected magnetic flux at the resonant surface.\cite{rf1993}
The complex quantity
\begin{equation}\label{e109}
{\mit\Delta\Psi}_s = \left[r\,\frac{\partial \delta\psi}{\partial r}\right]_{r_{s-}}^{r_{s+}}
\end{equation}
parameterizes the amplitude and phase of the current sheet flowing at the resonant surface.

@@

Simultaneously matching our separable solution of Eq.~(\ref{e3})  across the resonant surface and the wall yields\,\cite{rf1993}
\begin{align}
{\mit\Delta\Psi}_s& = E_{ss}\,{\mit\Psi}_s + E_{sw}\,{\mit\Psi}_w,\\[0.5ex]
{\mit\Delta\Psi}_w& = E_{ws}\,{\mit\Psi}_s+ E_{ww}\,{\mit\Psi}_w.
\end{align}
Here, $E_{ss}= [r\,d\hat{\psi}_s/dr]_{r_{s-}}^{r_{s+}}$,
$E_{ww}= [r\,d\hat{\psi}_w/dr]_{r_{w-}}^{r_{w+}}$,
$E_{sw} =[r\,{d\hat\psi}_w/dr]_{r=r_{s+}}$, and 
$E_{ws} =-[r\,{d\hat\psi}_s/dr]_{r=r_{w-}}$
are real quantities determined by the solutions of Eqs.~(\ref{e100}) and (\ref{e100a}) in the outer region.
It is easily demonstrated that 
$E_{sw} = E_{ws}$.\cite{rf1993}

Standard electromagnetic theory applied to the resistive wall reveals that\,\cite{nave,rf1993}
\begin{equation}
{\mit\Delta\Psi}_w = \tau_w\,\frac{d{\mit\Psi}_w}{dt},
\end{equation}
where
$\tau_w= \mu_0\,r_w\,\delta_w/\eta_w$.
Here, $\eta_w$ and $\delta_w$ are the electrical resistivity and radial thickness  of the wall, respectively.

Assuming an $\exp(-{\rm i}\,\omega\,t)$ time dependence of perturbed quantities, the previous four equations
can be combined to give
\begin{equation}
\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}= {\mit\Delta}_{pw} + \frac{{\mit\Delta}_{nw}-{\mit\Delta}_{pw}}{1-{\rm i}\,\omega\,\tau_{LR}},
\end{equation}
where ${\mit\Delta}_{pw}= E_{ss}$ is the  tearing stability index\cite{fkr} when the wall is perfectly conducting,
${\mit\Delta}_{nw} = E_{ss} + E_{sw}^{\,2}/(-E_{ww})$ is the  tearing stability index when there is no wall,
and $\tau_{LR}= \tau_w/(-E_{ww})$ is the effective L/R time of the wall. (Note that $E_{ww}<0$.)

@@

Our resonant plasma response model takes the form:\cite{fw}
\begin{align}
\frac{\partial\psi}{\partial\hat{t}}&= [\phi,\psi] -\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,[N,\psi]
+\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
\frac{\partial \hat{\nabla}^2\phi}{\partial \hat{t}}&= [\phi,\hat{\nabla}^2\phi] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right), \\[0.5ex]
\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\hat{\psi}] +\hat{d}_\beta^{\,2}\,[J,\psi]
+ \hat{D}_\parallel \,[[N,\hat{\psi}],\hat{\psi}]+ \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
\frac{\partial V}{\partial\hat{t}}&= [\phi,V] +[N,\psi] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V.\label{e21}
\end{align}
Here, $[A,B]\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot {\bf n}$, $\hat{t} = t/(r_s/V_A)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,r_s\,V_A)$, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$, 
$\hat{\chi}_\varphi= \chi_\varphi/(r_s\,V_A)$, where $\eta_{\parallel,\perp}$ is the parallel/perpendicular plasma electrical
resistivity at the resonant surface, $E_\parallel$ the parallel inductive electric field that maintains the equilibrium toroidal
plasma current in the vicinity of the resonant surface, and $\chi_\varphi$  the anomalous perpendicular ion momentum
diffusivity at the resonant surface. 
Moreover, $d_\beta=c_\beta\,d_i$, and $\hat{d}_\beta=d_\beta/r_s$, where $c_\beta = \sqrt{\beta/(1+\beta)}$, and
$\beta=(5/3)\,\mu_0\,p_0/B_z^{\,2}$. Here, $d_\beta$ is usually referred to as the {\em ion sound radius}. Furthermore,
$\lambda_e=0.71\,\eta_e/(1+\eta_e)$. Finally,\cite{fw}
\begin{align}
\hat{D}_\parallel&\equiv\frac{D_{\parallel}}{r_s\,V_A}= \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
\hat{D}_\perp& \equiv \frac{D_{\perp}}{r_s\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right),
\end{align}
where $\hat{\chi}_{\parallel\,e,i}=\chi_{\parallel\,e,i}/(r_s\,V_A)$,  $\hat{\chi}_{\perp\,e,i}=\chi_{\perp\,e,i}/(r_s\,V_A)$, 
$\chi_{\parallel\,e,i}$ is the parallel electron/ion energy diffusivity in the vicinity of the resonant surface, and 
$\chi_{\perp\,e,i}$ is the anomalous
electron/ion perpendicular energy diffusivity in the vicinity of the resonant surface.

@@

It is convenient  to work in a frame of reference that corotates with the tearing mode. In this reference frame, the
reconnected flux, ${\mit\Psi}_s$, is assumed to be a positive real
quantity. If $W$ is the full radial width of the magnetic island chain that develops at the resonant surface then it is
helpful to define the reduced island width:
\begin{equation}
w = \frac{W}{4}= \left(\frac{L_s\,{\mit\Psi}_s}{B_z}\right)^{1/2}.
\end{equation}
It is assumed that $w\ll r_s$. Let $\hat{w}=w/r_s$. 
 In the limit $|\hat{x}|/\hat{w}\gg 1$ (i.e., many island widths from the resonant surface), we have  
\begin{align}\label{e26}
\psi &\rightarrow \frac{\hat{x}^{\,2}}{2\,\hat{L}_s} + \frac{{\mit\Psi}_s}{r_s\,B_z}\,\cos\zeta,\\[0.5ex]
\phi &\rightarrow \left(\frac{\hat{\omega}}{m}- \hat{V}_E\right)\hat{x} - \frac{s}{4}\,\hat{V}_E'\,\hat{x}^{\,2},\\[0.5ex]
N &\rightarrow -\hat{V}_\ast\,\hat{x},\\[0.5ex]
V&\rightarrow \hat{V}_\parallel,\\[0.5ex]
J& \rightarrow -\frac{2}{q_s\,\hat{R}_0} + \frac{1}{\hat{L}_s}.\label{e30}
\end{align}
where 
$\hat{x}=(r-r_s)/r_s$,
 $\hat{L}_s=L_s/r_s$,  $L_s=R_0\,q_s/s_s$, $\hat{R}_0=R_0/r_s$, $\zeta=m\,\theta-n\,\varphi$, 
  $\hat{V}_E= V_E(r_s)/V_A$,
$\hat{V}_\ast= V_\ast(r_s)/V_A$,
$V_\ast(r) = (dp/dr)/(e\,n_0\,B_z)$ 
is the (dominant $\theta$-component of the) diamagnetic velocity,
 $\hat{V}_\parallel=\hat{d}_i\, V_z(r_s)/V_A$, $s_s=s(r_s)$, and $s(r)=d\ln q/d\ln r$. 
Here, $\omega = \hat{\omega}\,V_A/r_s$ is the rotation frequency of the tearing mode  in the
laboratory frame,
$s = {\rm sgn}(\hat{x})$,
and 
\begin{equation}
\hat{V}_E' = \frac{1}{V_A}\left[r\,\frac{dV_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
\end{equation}
The parameter $\hat{V}_E'$ is introduced  into the analysis in order to take into account the fact that the plasma rotation profile in the outer region develops a
gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that emerges 
at the surface. Finally, 
 $\hat{E}_\parallel =(2/s_s-1) \,(\hat{\eta}_\parallel/\hat{L}_s)$.

@@

Equations~(\ref{e469})--(\ref{e473}) must be solved subject to the boundary conditions [see Eqs.~(\ref{e26})--(\ref{e30})] 
\begin{align}
{\mit\Psi}&\rightarrow \frac{X^{2}}{2} + \cos\zeta,\label{e483}\\[0.5ex]
{\mit\Phi} &\rightarrow v\,X +\frac{ s\,v'\,X^{2}}{2},\label{e484}\\[0.5ex]
{\cal N}&\rightarrow X,\label{e486}\\[0.5ex]
{\cal V}&\rightarrow 0,\label{e486a}\\[0.5ex]
{\cal J}& \rightarrow 0,\label{e487}
\end{align}
as $|X|\rightarrow\infty$.  Here,
\begin{align}
v(T) &= \frac{\omega-\omega_E}{\omega_\ast},\label{e488}\\[0.5ex]
v'(T) &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.\label{e489}
\end{align}
Note that ${\mit\Psi}$, ${\mit\Phi}$, ${\cal N}$, ${\cal V}$, and ${\cal J}$ are all ${\cal O}(1)$ quantities.
Note, further,  that the boundary conditions (\ref{e483})--(\ref{e487}),
as well as the symmetry of Eqs.~(\ref{e469})--(\ref{e473}), ensure that ${\mit\Psi}$, ${\cal V}$, and
${\cal J}$ are even functions of $X$, whereas ${\mit\Phi}$ and ${\cal N}$ are odd functions.

\subsection{Ordering Scheme}
In the following, the dimensionless parameters $\epsilon_d$, $\epsilon_\beta$, $\epsilon_n$, $\epsilon_\eta$, $\epsilon_\chi$,
and $\epsilon_D$ are all assumed to be of similar size, but much smaller than unity. The orderings $\epsilon_n\ll 1$ and $\epsilon_\beta\ll 1$
are consistent with the standard large-aspect ratio, low-$\beta$ orderings used to describe conventional tokamak
plasmas. As will become apparent, the ordering $\epsilon_d\ll 1$ ensures that the island chain is
sufficiently wide that ion acoustic waves propagating parallel to the magnetic field are able to smooth out any
variations in the normalized electron number density, ${\cal N}$, around magnetic flux-surfaces.\cite{scott} The fact that $\epsilon_d\ll 1$ implies that
\begin{equation}
w \gg \rho_\beta,
\end{equation}
where
\begin{equation}
\rho_\beta = \left(\frac{L_s}{L_n}\right)d_\beta
\end{equation}
is a characteristic lengthscale that is of order the ion poloidal gyroradius. 
 The orderings $\epsilon_\eta\ll 1$, $\epsilon_\chi\ll 1$, and $\epsilon_D\ll 1$ ensure that the island
chain is sufficiently wide that the perpendicular diffusion of magnetic flux, momentum, and particles are not dominant
effects in the rescaled four-field equations. We shall also assume that $w/w_c\sim{\cal O}(1)$. In other words, the
island chain is sufficiently wide for the parallel diffusion of particles to compete with perpendicular diffusion.\cite{rff}

@@

\subsection{Flux-Surface Average Operator}
The {\em flux-surface average operator}, $\langle\cdots\rangle$, is defined\,\cite{rutherford}
\begin{equation}
\langle A(s,{\mit\Omega},\zeta)\rangle
\equiv \left\{
\begin{array}{llr}
\int_{\zeta_0}^{2\pi-\zeta_0}\frac{A(s,{\mit\Omega}\,\zeta)+A(-s,{\mit\Omega},\zeta)}{2\,[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}&~~~~~&0\leq {\mit\Omega}\leq 1\\[2ex]
\oint \frac{A(s,{\mit\Omega}\,\zeta)}{[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}
&&{\mit\Omega}> 1
\end{array}
\right.,
\end{equation}
where $\zeta_0=\cos^{-1}({\mit\Omega})$ and $0\leq\zeta_0\leq\pi$. 
It follows that
$\langle\{A,{\mit\Omega}\}\rangle = 0$
for {\em any}\/ $A(s,{\mit\Omega},\zeta,T)$. It is helpful to define
$\tilde{A}  \equiv A - \langle A\rangle/\langle 1\rangle$.
It follows that 
$\langle \tilde{A}\rangle =0$
 for {\em any}\/ $A(s,{\mit\Omega},\zeta,T)$.

@@

\section*{Disclaimer} This report was prepared as an account of work sponsored by an agency of the United States Government. Neither the United States Government nor any agency thereof, nor any of their employees, makes any warranty, express or implied, or assumes any legal liability or responsibility for the accuracy, completeness, or usefulness of any information, apparatus, product, or process disclosed, or represents that its use would not infringe privately owned rights. Reference herein to any specific commercial product, process, or service by trade name, trademark, manufacturer, or otherwise does not necessarily constitute or imply its endorsement, recommendation, or favoring by the United States Government or any agency thereof. The views and opinions of authors expressed herein do not necessarily state or reflect those of the United States Government or any agency thereof.

@@

>>>>

\subsection{Perturbed Magnetic Field}\label{cyl}
Consider a tearing mode perturbation that has $m$ periods in the poloidal direction, and
$n$ periods in the toroidal direction. 
The perturbed magnetic field associated with the tearing mode is written $\delta{\bf B} \simeq \nabla\delta\psi\times{\bf e}_z$,  
where
$\delta\psi(r,\theta,\varphi,t)= \delta\psi(r,t)\,\exp[\,{\rm i}\,(m\,\theta-n\,\varphi)]$, 
and $\varphi=z/R_0$ is a simulated toroidal angle. 
Throughout most of the plasma, $\delta\psi(r,t)$ satisfies the
{\em cylindrical tearing mode equation}:\cite{wes}
\begin{equation}\label{e3}
\frac{\partial^2\delta\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\delta\psi}{\partial r}-\frac{m^2}{r^2}\,\delta\psi - \frac{J_z'\,\delta\psi}{r\,(1/q-n/m)}=  0,
\end{equation}
where 
$J_z(r)= R_0\,\mu_0\,j_z(r)/B_z$,
and $j_z(r)$ is the equilibrium `toroidal' current density. Here, $'\equiv d/dr$.  Note that Eq.~(\ref{e3}) is singular at the so-called {\em resonant}\/ magnetic flux-surface, radius $r=r_s$, at which 
$q(r_s)= m/n$.

@@

As is well known, the general solution of Eq.~(\ref{e100}) is such that $\delta\psi$ is continuous across the resonant surface,
whereas $\partial\delta\psi/\partial r$ is discontinuous. The discontinuity in $\partial \delta\psi/\partial r$ implies the presence of a helical  current sheet  at the resonant surface. 
The complex quantity 
\begin{equation}\label{e108}
{\mit\Psi}_s(t)= \delta\psi(r_s,t) 
\end{equation}
parameterizes the amplitude and phase of the
reconnected magnetic flux at the resonant surface.\cite{rf1993}
The complex quantity
\begin{equation}\label{e109}
{\mit\Delta\Psi}_s = \left[r\,\frac{\partial \delta\psi}{\partial r}\right]_{r_{s-}}^{r_{s+}}
\end{equation}
parameterizes the amplitude and phase of the current sheet flowing at the resonant surface.

@@

Simultaneously matching our separable solution of Eq.~(\ref{e3})  across the resonant surface and the wall yields\,\cite{rf1993}
\begin{align}
{\mit\Delta\Psi}_s& = E_{ss}\,{\mit\Psi}_s + E_{sw}\,{\mit\Psi}_w,\\[0.5ex]
{\mit\Delta\Psi}_w& = E_{ws}\,{\mit\Psi}_s+ E_{ww}\,{\mit\Psi}_w.
\end{align}
Here, $E_{ss}= [r\,d\hat{\psi}_s/dr]_{r_{s-}}^{r_{s+}}$,
$E_{ww}= [r\,d\hat{\psi}_w/dr]_{r_{w-}}^{r_{w+}}$,
$E_{sw} =[r\,{d\hat\psi}_w/dr]_{r=r_{s+}}$, and 
$E_{ws} =-[r\,{d\hat\psi}_s/dr]_{r=r_{w-}}$
are real quantities determined by the solutions of Eqs.~(\ref{e100}) and (\ref{e100a}).
It is easily demonstrated that 
$E_{sw} = E_{ws}$.\cite{rf1993}

Standard electromagnetic theory applied to the resistive wall reveals that\,\cite{nave,rf1993}
\begin{equation}\label{e9}
{\mit\Delta\Psi}_w = \tau_w\,\frac{d{\mit\Psi}_w}{dt},
\end{equation}
where
$\tau_w= \mu_0\,r_w\,\delta_w/\eta_w$.
Here, $\eta_w$ and $\delta_w$ are the electrical resistivity and radial thickness  of the wall, respectively. 
In deriving Eq.~(\ref{e9}), we have made use of the so-called {\em thin wall}\/ approximation, according to
which the radial variation of $\delta\psi$ across the wall is negligible.  The thin wall approximation is
valid as long as
\begin{equation}
\frac{r_w}{\delta_w}\gg \tau_w\left|\frac{d\ln{\mit\Psi}_w}{dt}\right|.
\end{equation}

Assuming an $\exp(-{\rm i}\,\omega\,t)$ time dependence of perturbed quantities, the previous four equations
can be combined to give
\begin{equation}\label{e11}
\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}= {\mit\Delta}_{pw} + \frac{{\mit\Delta}_{nw}-{\mit\Delta}_{pw}}{1-{\rm i}\,\omega\,\tau_{LR}},
\end{equation}
where ${\mit\Delta}_{pw}= E_{ss}$ is the  tearing stability index\cite{fkr} when the wall is perfectly conducting,
${\mit\Delta}_{nw} = E_{ss} + E_{sw}^{\,2}/(-E_{ww})$ is the  tearing stability index when there is no wall,
and $\tau_{LR}= \tau_w/(-E_{ww})$ is the effective L/R time of the wall. (Note that $E_{ww}<0$.)

@@

Our resonant plasma response model takes the form:\,\cite{fw}
\begin{align}
\frac{\partial\psi}{\partial\hat{t}}&= [\phi,\psi] -\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,[N,\psi]
+\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
\frac{\partial \hat{\nabla}^2\phi}{\partial \hat{t}}&= [\phi,\hat{\nabla}^2\phi] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right), \\[0.5ex]
\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\hat{\psi}] +\hat{d}_\beta^{\,2}\,[J,\psi]
+ \hat{D}_\parallel \,[[N,\hat{\psi}],\hat{\psi}]+ \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
\frac{\partial V}{\partial\hat{t}}&= [\phi,V] +[N,\psi] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V.\label{e21}
\end{align}
Here, $[A,B]\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot {\bf n}$, $\hat{t} = t/(r_s/V_A)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,r_s\,V_A)$, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$, 
$\hat{\chi}_\varphi= \chi_\varphi/(r_s\,V_A)$, where $\eta_{\parallel,\perp}$ is the parallel/perpendicular plasma electrical
resistivity at the resonant surface, $E_\parallel$ the parallel inductive electric field that maintains the equilibrium toroidal
plasma current in the vicinity of the resonant surface, and $\chi_\varphi$  the (anomalous) perpendicular ion momentum
diffusivity at the resonant surface. 
Moreover, $d_\beta=c_\beta\,d_i$, and $\hat{d}_\beta=d_\beta/r_s$, where $c_\beta = \sqrt{\beta/(1+\beta)}$, and
$\beta=(5/3)\,\mu_0\,p_0/B_z^{\,2}$. Here, $d_\beta$ is usually referred to as the {\em ion sound radius}. Furthermore,
$\lambda_e=0.71\,\eta_e/(1+\eta_e)$. Finally,\cite{fw}
\begin{align}
\hat{D}_\parallel&\equiv\frac{D_{\parallel}}{r_s\,V_A}= \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
\hat{D}_\perp& \equiv \frac{D_{\perp}}{r_s\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right),
\end{align}
where $\hat{\chi}_{\parallel\,e,i}=\chi_{\parallel\,e,i}/(r_s\,V_A)$,  $\hat{\chi}_{\perp\,e,i}=\chi_{\perp\,e,i}/(r_s\,V_A)$, 
$\chi_{\parallel\,e,i}$ is the parallel electron/ion energy diffusivity in the vicinity of the resonant surface, and 
$\chi_{\perp\,e,i}$ is the anomalous
electron/ion perpendicular energy diffusivity in the vicinity of the resonant surface.

@@

It is convenient  to work in a frame of reference that corotates with the tearing mode. In this reference frame, the
reconnected flux, ${\mit\Psi}_s$, is assumed to be a positive real
quantity. If $W$ is the full radial width of the magnetic island chain that develops at the resonant surface then it is
helpful to define the reduced island width:
\begin{equation}\label{e26a}
w = \frac{W}{4}= \left(\frac{L_s\,{\mit\Psi}_s}{B_z}\right)^{1/2}.
\end{equation}
It is assumed that $w\ll r_s$. Let $\hat{w}=w/r_s$. 
 In the limit $|\hat{x}|/\hat{w}\gg 1$ (i.e., many island widths from the resonant surface), we have  
\begin{align}\label{e26}
\psi &\rightarrow \frac{\hat{x}^{\,2}}{2\,\hat{L}_s} + \frac{{\mit\Psi}_s}{r_s\,B_z}\,\cos\zeta,\\[0.5ex]
\phi &\rightarrow \left(\frac{\hat{\omega}}{m}- \hat{V}_E\right)\hat{x} - \frac{s}{4}\,\hat{V}_E'\,\hat{x}^{\,2},\\[0.5ex]
N &\rightarrow -\hat{V}_\ast\,\hat{x},\\[0.5ex]
V&\rightarrow \hat{V}_\parallel,\\[0.5ex]
J& \rightarrow -\frac{2}{q_s\,\hat{R}_0} + \frac{1}{\hat{L}_s}.\label{e30}
\end{align}
where 
$\hat{x}=(r-r_s)/r_s$,
 $\hat{L}_s=L_s/r_s$,  $L_s=R_0\,q_s/s_s$, $\hat{R}_0=R_0/r_s$, $\zeta=m\,\theta-n\,\varphi$, 
  $\hat{V}_E= V_E(r_s)/V_A$,
$\hat{V}_\ast= V_\ast(r_s)/V_A$,
$V_\ast(r) = (dp/dr)/(e\,n_0\,B_z)$ 
is the (dominant $\theta$-component of the) diamagnetic velocity,
 $\hat{V}_\parallel=\hat{d}_i\, V_z(r_s)/V_A$, $s_s=s(r_s)$, and $s(r)=d\ln q/d\ln r$. 
Here, $\omega = \hat{\omega}\,V_A/r_s$ is the rotation frequency of the tearing mode  in the
laboratory frame,
$s = {\rm sgn}(\hat{x})$,
and 
\begin{equation}
\hat{V}_E' = \frac{1}{V_A}\left[r\,\frac{dV_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
\end{equation}
The parameter $\hat{V}_E'$ is introduced  into the analysis in order to take into account the fact that the plasma rotation profile in the outer region develops a
gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that emerges 
at the surface.\cite{fw} Finally, 
 $\hat{E}_\parallel =(2/s_s-1) \,(\hat{\eta}_\parallel/\hat{L}_s)$.

@@

Equations~(\ref{e469})--(\ref{e473}) must be solved subject to the boundary conditions [cf.\ Eqs.~(\ref{e26})--(\ref{e30})] 
\begin{align}
{\mit\Psi}&\rightarrow \frac{X^{2}}{2} + \cos\zeta,\label{e483}\\[0.5ex]
{\mit\Phi} &\rightarrow v\,X +\frac{ s\,v'\,X^{2}}{2},\label{e484}\\[0.5ex]
{\cal N}&\rightarrow X,\label{e486}\\[0.5ex]
{\cal V}&\rightarrow 0,\label{e486a}\\[0.5ex]
{\cal J}& \rightarrow 0,\label{e487}
\end{align}
as $|X|\rightarrow\infty$.  Here,
\begin{align}
v &= \frac{\omega-\omega_E}{\omega_\ast},\label{e488}\\[0.5ex]
v' &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.\label{e489}
\end{align}
Note that ${\mit\Psi}$, ${\mit\Phi}$, ${\cal N}$, ${\cal V}$, and ${\cal J}$ are all ${\cal O}(1)$ quantities.
Note, further,  that the boundary conditions (\ref{e483})--(\ref{e487}),
as well as the symmetry of Eqs.~(\ref{e469})--(\ref{e473}), ensure that ${\mit\Psi}$, ${\cal V}$, and
${\cal J}$ are even functions of $X$, whereas ${\mit\Phi}$ and ${\cal N}$ are odd functions.

\subsection{Ordering Scheme}
In the following, the dimensionless parameters $\epsilon_d$, $\epsilon_\beta$, $\epsilon_n$, $\epsilon_\eta$, $\epsilon_\chi$,
and $\epsilon_D$ are all assumed to be of similar size, but much smaller than unity. The orderings $\epsilon_n\ll 1$ and $\epsilon_\beta\ll 1$
are consistent with the standard large-aspect ratio, low-$\beta$ orderings used to describe conventional tokamak
plasmas. As will become apparent, the ordering $\epsilon_d\ll 1$ ensures that the island chain is
sufficiently wide that ion acoustic waves propagating parallel to the magnetic field are able to smooth out any
variations in the normalized electron number density, ${\cal N}$, around magnetic flux-surfaces.\cite{scott} The fact that $\epsilon_d\ll 1$ implies that
$w \gg \rho_\beta$,
where
\begin{equation}
\rho_\beta = \left(\frac{L_s}{L_n}\right)d_\beta
\end{equation}
is a characteristic lengthscale that is of order the ion poloidal gyroradius. 
 The orderings $\epsilon_\eta\ll 1$, $\epsilon_\chi\ll 1$, and $\epsilon_D\ll 1$ ensure that the island
chain is sufficiently wide that the perpendicular diffusion of magnetic flux, momentum, and particles are not dominant
effects in the rescaled resonant response equations. We shall also assume that $w/w_c\sim{\cal O}(1)$. In other words, the
island chain is sufficiently wide for the parallel diffusion of particles to compete with perpendicular diffusion.\cite{rff}

@@

\subsection{Flux-Surface Average Operator}
The {\em flux-surface average operator}, $\langle\cdots\rangle$, is defined\,\cite{rutherford}
\begin{equation}
\langle A(s,{\mit\Omega},\zeta)\rangle
\equiv \left\{
\begin{array}{llr}
\int_{\zeta_0}^{2\pi-\zeta_0}\frac{A(s,{\mit\Omega}\,\zeta)+A(-s,{\mit\Omega},\zeta)}{2\,[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}&~~~~~&0\leq {\mit\Omega}\leq 1\\[2ex]
\oint \frac{A(s,{\mit\Omega}\,\zeta)}{[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}
&&{\mit\Omega}> 1
\end{array}
\right.,
\end{equation}
where $\zeta_0=\cos^{-1}({\mit\Omega})$ and $0\leq\zeta_0\leq\pi$. 
It follows that
$\langle\{A,{\mit\Omega}\}\rangle = 0$
for any $A(s,{\mit\Omega},\zeta,T)$. It is helpful to define
$\tilde{A}  \equiv A - \langle A\rangle/\langle 1\rangle$.
It follows that 
$\langle \tilde{A}\rangle =0$
 for any $A(s,{\mit\Omega},\zeta,T)$.

@@

@@

\bibitem{white} R.A.~White, D.A.~Monticello, M.N.~Rosenbluth, and B.V.~Waddell, Phys.\ Fluids {\bf 20}, 800 (1977).

\bibitem{thy} A.~Thyagaraja, Phys.\ Fluids {\bf 24}, 1716 (1981).

\bibitem{esc} D.F.~Escande, and M.~Ottaviani, Phys. Lett.\ A {\bf 323}, 278 (2004).

\bibitem{mit} F.~Militello, and F.~Porcelli, Phys.\ Plasmas {\bf 1}, L13 (2004).

\bibitem{has} R.J.~Hastie, F.~Militello, and F.~Porcelli, Phys.\ Rev.\ Lett.\ {\bf 95}, 065001 (2005).
